%%%%% STYLES AND STUFF 
\include{includes/style}

\begin{document}


%%%%% FRONT STUFF	
\frontmatter

\begin{titlepage}

\begin{center}
\vspace*{3ex}
\textbf{\Huge Inferring Interestingness in Online Social Networks}\\[2ex]
\textbf{\large A thesis submitted in partial fulfilment}\\[1ex]
\textbf{\large of the requirement for the degree of Doctor of Philosophy}\\[16ex]
\textbf{\LARGE William M. Webberley}\\
\vfill
\textbf{\LARGE May 2014}\\
\vfill
\textbf{\LARGE Cardiff University}\\[1ex]
\textbf{\LARGE School of Computer Science \& Informatics}\\[4ex]
\end{center}

\end{titlepage}

\newpage\thispagestyle{empty}\cleardoublepage


\thispagestyle{plain}

\vspace*{6ex}

\textbf{\large Declaration}

This work has not previously been accepted in substance for any degree and is not concurrently submitted in candidature for any degree.\\[2ex]
Signed \dotfill \ (candidate) \hspace*{10em}\\[1ex]
Date\ \ \ \ \ \dotfill \hspace*{18em}

\vfill

\textbf{\large Statement 1}

This thesis is being submitted in partial fulfilment of the requirements for the degree of PhD.\\[2ex]
Signed \dotfill \ (candidate) \hspace*{10em}\\[1ex]
Date\ \ \ \ \ \dotfill \hspace*{18em}

\textbf{\large Statement 2}

This thesis is the result of my own independent work/investigation,
except where otherwise stated. Other sources are acknowledged by
explicit references.\\[2ex]
Signed \dotfill \ (candidate) \hspace*{10em}\\[1ex]
Date\ \ \ \ \ \dotfill \hspace*{18em}

\vfill

\textbf{\large Statement 3}

I hereby give consent for my thesis, if accepted, to be available for photocopying and for inter-library loan,
 and for the title and summary to be made available to outside organisations.\\[2ex]
Signed \dotfill \ (candidate) \hspace*{10em}\\[1ex]
Date\ \ \ \ \ \dotfill \hspace*{18em}

\vfill

\cleardoublepage


%\thispagestyle{plain}
%\ \vfill{\small
%Copyright \copyright\ 2014 Will Webberley.\\
%Permission is granted to copy, distribute and/or modify this document
%under the terms of the GNU Free Documentation License, Version 1.3\footnote{http://www.gnu.org/copyleft/fdl.html} or
%any later version published by the Free Software Foundation; with no
%Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts}\\[3.5ex]
%\cleardoublepage


\ \vspace*{1.11cm}
\markboth{Dedication}{}
\begin{flushright}
\textbf{\large To my family and friends;}\\
\textbf{\large To George, Pete,}\\
\textbf{\large Jack, Max, Ella,}\\
\textbf{\large Tom, and Charlie.}\\
\large This is for their support.
\end{flushright}
\newpage
\markboth{}{}
\cleardoublepage

\chapter*{Acknowledgements}
This thesis and the research it contains could not exist if not for the unfailing support of my supervisors, Roger Whitaker and, particularly, Stuart Allen. Their guidance and input have provided drive, shaped my research and have given me the confidence required for producing and defending ideas both within and outside of research. My utmost gratitude is extended to them for this and for their continual encouragement at all stages of my PhD, always with fresh perspective and clarification for research pathways and for keeping me on track. I feel confident in saying that I was very lucky in being in their supervision and I would not be the same person, professionally and otherwise, today if it wasn't for their combined inputs over the past few years.

I'd also like to thank Martin Chorley for his continuously helpful and enthusiastic crowdsourcing expertise, without which the research in this thesis could not have been validated in the way it has been. Matt Williams has provided insight throughout my time as a PhD student, from long sessions discussing the tiniest irrelevant details to recommendations on research direction and scope. Discussions with him have helped form many of my research ideas. I am also deeply grateful to Chris Gwilliams for his helpful input over course of my PhD, including information on where one might find the most cost-effective M.O.T. deals through to how best to structure complex and fiddly data queries. Thanks also to Matt John, who, ever critical, helped proof-read this thesis and provided invaluable constructive feedback on notation and nomenclature.

My family and close friends have always pushed me and provided encouragement to make me who I am today. If not for them, I would not have had the confidence to carry out and defend my research. They deserve my utmost thanks.

Finally, my time as a research student would not have been the same without the constant presence and support from the School of Computer Science \& Informatics, the other members of the MobiSoc group, the `superteam', and non-academic friends. In addition to those named previously, Gualtiero Colombo, Ian Cooper, Jon Quinn, Diego Pizzocaro, Rich Coombs, Liam Turner, Nick Sharp, and Ross Taylor have made the time spent researching my PhD both interesting and enjoyable and I am extremely grateful to them.





\chapter*{Abstract}
Information sharing and user-generated content on the Internet has given rise to the increased presence of uninteresting and `noisy' information in media streams on many online social networks. Although there is a lot of `interesting' information also shared amongst users, the noise increases the cognitive burden in terms of the users' abilities to identify what is interesting and may increase the chance of missing content that is useful or important.
Additionally, users on such platforms are generally limited to receiving information only from those that they are directly linked to on the social graph, meaning that users exist within distinct content `bubbles', further limiting the chance of receiving interesting and relevant information from outside of the immediate social circle. 
In this thesis, Twitter is used as a platform for researching methods for deriving ``interestingness'' through popularity as given by the mechanism of \textit{retweeting}, which allows information to be propagated further between users on Twitter's social graph. Retweet behaviours are studied, and features; such as those surrounding Tweet audience, information redundancy, and propagation depth through path-length, are uncovered to help relate retweet action to the underlying social graph and the communities it represents. This culminates in research into a methodology for assigning scores to Tweets based on their `quality', which is validated and shown to perform well in various situations.


\tableofcontents
\input{includes/listofpublications}
\listoffigures
\listoftables
\input{includes/acronyms}
\input{includes/glossary}

%%%%% MAIN STUFF 
\mainmatter 

\include{1.Introduction/intro}
\include{2.Background/background}
\include{3.Chapter1/chapter1}
\include{4.Chapter2/chapter2}
\include{5.Chapter3/chapter3}
\include{6.Conclusions/conclusions}

%%%%% BACK STUFF 
\backmatter

\def\baselinestretch{1.24}\normalfont

\bibliographystyle{plainnat}
\bibliography{includes/library}

\end{document}
